\documentclass[12pt]{article}
\usepackage{times}
\usepackage{fullpage}
\usepackage{amsfonts}

\setlength{\parindent}{0in}
\setlength{\parskip}{0.1in}

\begin{document}

\thispagestyle{empty}

{\large CS3311 Homework 2} \hfill
Due date: {\bf Monday}, September 16, 2019, 8:59am\\
\hfill
Submission: Typed, on Canvas (scanned submissions are not allowed)
\vspace{-0.1in}

\rule{\textwidth}{0.5mm}
\begin{small}
The answers must be the original work of the author.  While discussion
with others is permitted and encouraged, the final work should be done
individually. You are not allowed to work in groups.  You are allowed to
build on the material supplied in the class. Any other source must be
specified clearly.
\end{small}
\rule{\textwidth}{0.5mm}

{\bf 1.} {\em (100 points)} 

Consider the set $S_1$ constructed recursively. 
The first member of the basis sequence is a number, and the second
member is a string. The recursive step performs an arithmetic addition on the 
first member and a string concatenation on the second member.
The symbols $a, b$ are characters, not variables.
\begin{quote}
{\bf (i) Basis:} $[1,a] \in S_1$ and $[1,b] \in S_1$

{\bf (ii) Recursive step:} If $[n,w] \in S_1$, then 
$[n+2, awa] \in S_1$ and $[n+2, bwb] \in S_1$.

{\bf (iii) Closure:} $S_1$ consists of exactly the elements that can be
obtained by starting with the basis elements of $S_1$ and applying the
recursive step finitely many times to construct new elements of $S_1$.
\end{quote}

Use induction to prove that the first member of each pair represents the
length of the string which is the second member. 
In other words, for all $[n,m] \in S_1 \; n=$length$(m)$.

The induction proof should present the following three components clearly:
  \begin{quote}
    Basis \\
    Inductive hypothesis \\
    Inductive step
  \end{quote}
{\bf(1)}
\begin{quote}
 {\bfseries {Basis:}}
 The first members in the set is $[1,a]$ and $[1,b]$.  $1$=length$(a)$ and $1$=length$(b)$ therefor the basis of induction holds\\
 {\bfseries {Inductive hypothesis:}} Assume that each member of $S_1$ which has been formed by applying the recursive step n times, are in the form $[n,m] $ and has the property that$  n=$length$(m)$ property \\
{\bfseries Inducive step:}
let $\omega$ be an element in $S_1$  that was made by applying the recursive step n time, $\omega$ is of the form $[n,m] $ and has the property that  $ n = $length$(m)$. The next element,$x$ that will be added to set $S_1$ after $n+1$ steps. To obtain $y$ apply the recurisve step once on $\omega$. $y= [n+2,ama]$ or $y= [n+2,bmb]$. Both definitions add 2 to $n$ and grows the length of $m$ by two. That means that if $n =$ length$(m)$ then $n+2 = $length$(cmc)$ where c is either a or b. we assumed  $n =$ length$(m)$ in the inductive hypothesis and therefor, conclude by mathematical induction that for all $[n,m] \in S_1 \; n= $length$(m)$.
\end{quote}
\end{document}
